---
title: "ISSP Initial Analysis"
author: "Maddie Wettach, Samantha Ho and Simon Halliday"
date: "2018-March -22"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#test to make sure problem is solved
```


## Requrements for the analysis we do
Make sure that you have these packages installed. If you don't have them installed, then run `install.packages("packagename")` in the R command line (not in this R Markdown file) to install them on your computer. 
```{r requirements, warning = FALSE, message = FALSE}
library(tidyverse)
library(haven)
library(stargazer)
library(mosaic)
library(readxl)
```

## Read in the data
Maddie/Samantha: I didn't check whether I've labeled these correctly, but I presumed that the data with later versions (v2.1) is the one for 2005. Am I right? 

```{r read_data}
ISSP05 <- read_stata("../Data/OriginalData/ZA4350_v2-0-0.dta")
ISSP15 <- read_stata("../Data/OriginalData/ZA6770_v2-1-0.dta")
```

```{r}
PPPcodes <- read_csv("../Data/SNA_TABLE4_27032018185918382.csv")
PPPWB <- read_csv("../Data/API_PA.NUS.PPP_DS2_en_csv_v2.csv")
WBERs <- read_csv("../Data/officialexchangerate.csv")
CountryCodes <- read_xlsx("../Data/country_codes.xlsx", col_names = TRUE)
```

We need to select down the WB Exchange Rates just to 2015 and country codes. 
```{r}
WBER15 <- 
  WBERs %>% 
  select(`Country Code`, `2015`) %>% 
  rename(c_alphan3 = `Country Code`, 
         exchangrate = `2015`)
```

Here we create a new object and select down just to the variables we need for the individual income analysis. 
```{r}
income15 <- 
  ISSP15 %>%
  select(country, c_alphan, CASEID, contains("_RINC"))
```

```{r}
narInc <- 
  income15 %>%
  gather(code, value, -CASEID, -country, -c_alphan) 
```

```{r}
narInc <- 
  narInc %>% 
  mutate(value = ifelse(value %in% c(999990, 999996, 999997, 999998, 999999, 
                                     9999990, 9999996, 9999997, 9999998, 9999999, 
                                     99999990, 99999996, 99999998, 99999997, 99999999), NA, value))
```

```{r}
narInc <- 
  narInc %>% 
  filter(complete.cases(value))
```

```{r}
sumInc <- 
  narInc %>% 
  group_by(country) %>% 
  summarise(meaninc = mean(value))
countries <- sumInc$country
```


```{r}
PPPcodes <- 
  PPPcodes %>%
  mutate(c_alphan3 = LOCATION) %>%
  left_join(CountryCodes, by = "c_alphan3")
```



```{r}
PPPWB <- 
  PPPWB %>%
  mutate(c_alphan3 = `Country Code`) 
PPPWBsel <- 
  PPPWB %>% 
  select(`2015`, c_alphan3) %>% 
  rename(PPP2015 = `2015`) %>% 
  left_join(CountryCodes, by = "c_alphan3") %>%
  filter(country %in% countries)
sumInc <- 
  sumInc %>%
  left_join(PPPWBsel, by = "country") 
sumInc <- 
  sumInc %>%
  left_join(WBER15, by = "c_alphan3") %>% 
  arrange(c_alphan)
countrycodes <- sumInc$c_alphan 
```

We now need to define the period over which the income is measured because the income is either annual or monthly depending on the country. 

```{r}
sumInc <- 
  sumInc %>% 
  mutate(inctype = ifelse(c_alphan %in% c("CN", "DK", "JP", "NO", "NZ", "US"), "annual", "monthly"),
         incadj = ifelse(inctype == "annual", 12, 1))
```



```{r, eval = F}
sumInc <-
  sumInc %>%
  mutate(exchangerate = ifelse(c_alphan3 %in% c("AUT", "BEL", "BRG", "HRV", "CYP", "CZE", 
                                                "DNK", "EST", "FIN", "FRA", "DEU", "GRC",
                                                "HUN", "IRL", "ITA", "LVA", "LTU", "LUX",
                                                "MLT", "NLD", "POL", "PRT", "ROU", "SVK",
                                                "SVN", "ESP", "SWE"), 0.9016590, exchangerate))
```

We need to filter out Venezuela (VE) and Taiwan (TW) because of missing data we need (the PPP rates for conversion of income)
```{r filter_out_VE_TW}
sumInc <- 
  sumInc %>% 
  filter(!country %in% c(158,862)) 
```


```{r}
IncComp <- 
  sumInc %>% 
  mutate(pppinc = meaninc/PPP2015, 
         monthinc = pppinc/incadj)
```


```{r}
IncComp %>% 
  ggplot(aes(x = reorder(c_alphan3, monthinc), y = monthinc)) + 
  geom_bar(stat = "identity",  fill = "#31a354") + #The color is defined by hexadecimal code here that I grabbed from colorbrewer2.org
  theme(#axis.text.y = element_text(angle = 45, hjust = 1), 
        text = element_text(size = 10)) + 
  ylab("PPP Converted Individual Reported Income, 2015 USD") + 
  xlab("") + #We don't realy need a label for the countries
  coord_flip() + # Testing what it looks like to have countries on the vertical axis
  theme_bw() + 
  labs(title = "Personally Reported Individual Monthly Income",  
       subtitle = "Source: ISSP, 2015", 
       caption = "(Note: Work in progress. Some incomes are gross and others are net of taxes)")
ggsave(file = "../figures/country_ind_income.png", width = 8, height = 6, units = c("in"), dpi = 300)
```


Next, what are the variables that we want to look at: 
```{r}
tally(~v2, data = ISSP15)
```
New variables for analysis: General satisfaction, Pride in firm , Pride in occupation, Stress
```{r}
satis15 <- ISSP15 %>% select(country, c_alphan, CASEID, v44)
firmpride15 <- ISSP15 %>% select(country, c_alphan, CASEID, v46)
jobpride15 <- ISSP15 %>% select(country, c_alphan, CASEID, v49)
stress15 <- ISSP15 %>% select(country, c_alphan, CASEID, v31)
```

Replace missing values with NA
```{r}
satis15 <- satis15 %>% mutate(v44 = ifelse(v44 %in% c(0, 8, 9), NA, v44))
firmpride15 <- firmpride15 %>% mutate(v46 = ifelse(v46 %in% c(0, 8), NA, v46))
jobpride15 <- jobpride15 %>% mutate(v49 = ifelse(v49 %in% c(0, 8), NA, v49))
stress15 <- stress15 %>% mutate(v31 = ifelse(v31 %in% c(0, 8), NA, v31))
```

Create df with summaries of new variables
```{r}
sum15 <- firmpride15 %>% 
          group_by(country) %>%
          summarise(meanfp = mean(v46, na.rm = TRUE))
sumsat15 <- satis15 %>%
          group_by(country) %>%
          summarise(meansat = mean(v44, na.rm = TRUE))
sumjp15 <- jobpride15 %>%
          group_by(country) %>%
          summarise(meanjp = mean(v49, na.rm = TRUE))
sumstr15 <- stress15 %>%
          group_by(country) %>%
          summarise(meanstr = mean(v31, na.rm = TRUE))

sum15 <- sum15 %>%
        left_join(sumsat15, by = "country")
sum15 <- sum15 %>%
        left_join(sumjp15, by = "country")
sum15 <- sum15 %>%
        left_join(sumstr15, by = "country")
```


Simon: I'm adding Maddie's sum15 to the sumInc data that I already created: 
```{r}
sumInc <- 
  sumInc %>% 
  left_join(sum15, by = "country")
```


